Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-06-01 analysis/preregistration_template.Rmd
Update analysis/preregistration_template.Rmd
move in-text comment to GH comment

*Describe how you will separate and distinguish between raw data, manipulated data, and outputs from modelling or any analyses of the model.* HF - Not sure exactly what this means

>>>>

*Describe how you will separate and distinguish between raw data, manipulated data, and outputs from modelling or any analyses of the model.*
